Study Comparison

### 2023-08-22 analysis/aud_analysis.Rmd
minor graphical changes

# weekly coughs per min by class and condition
coughs_pl <- coughs %>%
  mutate(week = isoweek(date)) %>%
  filter(week != 6) %>%
  mutate(week = ifelse(week < 6, week - min(week) + 1, week - min(week))) %>%
  group_by(class, week) %>%
  summarize(coughs_per_min = sum(n_coughs) / sum(TT),
            aircleaner = first(aircleaner)) %>%
  ungroup() %>%
  mutate(aircleaner = factor(aircleaner, levels = c("Yes", "No")),
         class = factor(class, levels = c("A", "B"))) %>%
  arrange(class, aircleaner) %>%
  ggplot(aes(x = factor(week), y = coughs_per_min, fill = aircleaner, pattern = class)) +
  geom_bar_pattern(stat = "identity", color = "black", pattern_fill = "white", pattern_angle = 45,
                   pattern_density = 0.25, pattern_spacing = 0.05, width = .5) +
  labs(x = "Study week", y = "Number of coughs per min", fill = "Air cleaner", pattern = "Class", title = "A") +
  scale_fill_manual(values = rev(wes_palette("Royal1")[1:2])) +
  scale_x_discrete(breaks = 1:7) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)), breaks = seq(0, 10, 2)) +
  scale_pattern_manual(values = c(A = "stripe", B = "none")) +
  theme_custom() +
  theme(legend.position = "top",
        legend.direction = "horizontal",
        legend.key.width = unit(0.5, "cm"),
        legend.key.height = unit(0.3, "cm"),
        plot.title.position = "plot") +
  guides(fill = guide_legend(nrow = 1, override.aes = list(pattern = "none", order = 2)),
         pattern = guide_legend(nrow = 1, override.aes = list(fill = "white"), order = 1))

@@

theta_pl <- draws_theta %>%
  ggplot(aes(y = v, x = rr, color = v)) +
  geom_vline(aes(xintercept = 1), linetype = "dotted", color = "red") +
  stat_pointinterval(shape = 21, fill = "white") +
  scale_color_manual(values = wes_palette("IsleofDogs1")) +
  labs(x = "Relative risk ratio", title = "B") +
  theme_custom() +
  theme(axis.title.y = element_blank(), legend.position = "none",
        plot.title.position = "plot")

>>>>

# weekly coughs per min by class and condition
coughs_pl <- coughs %>%
  mutate(week = isoweek(date)) %>%
  filter(week != 6) %>%
  mutate(week = ifelse(week < 6, week - min(week) + 1, week - min(week))) %>%
  group_by(class, week) %>%
  summarize(coughs_per_min = sum(n_coughs) / sum(TT),
            aircleaner = first(aircleaner)) %>%
  ungroup() %>%
  mutate(aircleaner = factor(aircleaner, levels = c("Yes", "No")),
         class = factor(class, levels = c("A", "B"))) %>%
  arrange(class, aircleaner) %>%
  ggplot(aes(x = factor(week), y = coughs_per_min, fill = aircleaner, pattern = class)) +
  geom_bar_pattern(stat = "identity", color = "black", pattern_fill = "white", pattern_angle = 45,
                   pattern_density = 0.25, pattern_spacing = 0.05, width = .5) +
  labs(x = "Study week", y = "Number of coughs per min", fill = "Air cleaner", pattern = "Class", title = "a") +
  scale_fill_manual(values = rev(wes_palette("Royal1")[1:2])) +
  scale_x_discrete(breaks = 1:7) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)), breaks = seq(0, 10, 2)) +
  scale_pattern_manual(values = c(A = "stripe", B = "none")) +
  theme_custom() +
  theme(legend.position = "top",
        legend.direction = "horizontal",
        legend.key.width = unit(0.5, "cm"),
        legend.key.height = unit(0.3, "cm"),
        plot.title.position = "plot") +
  guides(fill = guide_legend(nrow = 1, override.aes = list(pattern = "none", order = 2)),
         pattern = guide_legend(nrow = 1, override.aes = list(fill = "white"), order = 1))

@@

theta_pl <- draws_theta %>%
  ggplot(aes(y = v, x = rr, color = v)) +
  geom_vline(aes(xintercept = 1), linetype = "dotted", color = "red") +
  stat_pointinterval(shape = 21, fill = "white") +
  scale_color_manual(values = wes_palette("IsleofDogs1")) +
  labs(x = "Relative risk", title = "b") +
  theme_custom() +
  theme(axis.title.y = element_blank(), legend.position = "none",
        plot.title.position = "plot")

### 2023-08-22 analysis/mol_analysis.Rmd
minor graphical changes

# plot
res_pl <- res  %>%
  ggplot() +
  stat_pointinterval(aes(x = beta1, y = lag), point_fill = "white", shape = 21, point_size = 3, .width = c(0.5, 0.8, 0.95)) +
  geom_vline(aes(xintercept = 1), linetype = "dashed") +
  scale_x_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0)), breaks = seq(0, 2, .25)) +
  scale_size_continuous(range = c(1, 9)) +
  labs(x = "Relative risk ratio", y = "Lag of sampling results", fill = "CrI") +
  theme_custom() +
  theme(legend.position = "top", legend.direction = "horizontal",
        legend.key.height = unit(.25, "cm"), legend.key.width = unit(.35, "cm"))
res_pl
save_plot(res_pl, pdf_file = "../results/mol-data/model-results.pdf", w = 10, h = 6)
```

>>>>

# plot
res_pl <- res  %>%
  ggplot() +
  stat_pointinterval(aes(x = beta1, y = lag), point_fill = "white", shape = 21, point_size = 3, .width = c(0.5, 0.8, 0.95)) +
  geom_vline(aes(xintercept = 1), linetype = "dashed") +
  scale_x_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0)), breaks = seq(0, 2, .25)) +
  scale_size_continuous(range = c(1, 9)) +
  labs(x = "Relative risk", y = "Lag of sampling results", fill = "CrI") +
  theme_custom() +
  theme(legend.position = "top", legend.direction = "horizontal",
        legend.key.height = unit(.25, "cm"), legend.key.width = unit(.35, "cm"))
res_pl
save_plot(res_pl, pdf_file = "../results/mol-data/model-results.pdf", w = 10, h = 6)
```

### 2023-08-22 analysis/study_comaprison.Rmd
minor graphical changes

```{r}
rr <- data.frame(
  year = factor(c(rep(2022, 3), rep(2023, 3)), levels = c(2022, 2023)),
  interval = rep(c("Mean", "Lower", "Upper"), times = 2),
  estimate = c(c(1.00, 0.22, 2.067), c(0.72, 0.44, 1.15))
) %>%
  dcast(year ~ interval) %>%
  ggplot(aes(y = year, color = year)) +
  geom_vline(aes(xintercept = 1), linetype = "dashed") +
  geom_errorbar(mapping = aes(xmin = Lower, xmax = Upper), lineend = "square", size = 1, width = .05) +
  geom_point(mapping = aes(x = Mean), shape = 23, size = 2, fill = "white") +
  labs(y = "Study year", x = "Adjusted risk ratio (%)", title = "d") + 
  scale_color_manual(values = wes_palette("Darjeeling2")[c(2, 5)]) +
  theme_custom() +
  theme(legend.position = "none",
        plot.title.position = "plot")

>>>>

```{r}
rr <- data.frame(
  year = factor(c(rep(2022, 3), rep(2023, 3)), levels = c(2022, 2023)),
  interval = rep(c("Mean", "Lower", "Upper"), times = 2),
  estimate = c(c(1.00, 0.22, 2.067), c(0.72, 0.44, 1.15))
) %>%
  dcast(year ~ interval) %>%
  ggplot(aes(y = year, color = year)) +
  geom_vline(aes(xintercept = 1), linetype = "dashed") +
  geom_errorbar(mapping = aes(xmin = Lower, xmax = Upper), lineend = "square", size = 1, width = .05) +
  geom_point(mapping = aes(x = Mean), shape = 23, size = 2, fill = "white") +
  labs(y = "Study year", x = "Adjusted relative risk (%)", title = "d") + 
  scale_color_manual(values = wes_palette("Darjeeling2")[c(2, 5)]) +
  theme_custom() +
  theme(legend.position = "none",
        plot.title.position = "plot")
